### 2012-10-24 paper_sean/results.tex
final changes in figure before handing it over to jeff

\figp{final_sean_kyrre_fitness}{0.92}
{Fitnesses of the champion gaits evolved with HyperNEAT and a genetic algorithm
averaged over 20 runs, measured in distance travelled over 12 seconds
in cm/s. The dashed lines are standard deviations. HyperNEAT gaits outperformed gaits evolved in simulation using a
genetic algorithm~\cite{glette} by 54.3\% in simulation and 5.4\% in
reality, and they outperformed gaits evolved using HyperNEAT in
hardware by 49.5\% (\tabref{results}).}

>>>>

\figp{FINAL_kyrre_sean_fitness}{0.92}
{Fitnesses of the champion gaits evolved with HyperNEAT and a genetic
algorithm~\cite{glete} averaged over 20 runs, measured in simulation
as distance travelled over 12 seconds in cm/s. The dashed lines are
standard deviations. HyperNEAT gaits outperformed gaits evolved in
simulation using a genetic algorithm~\cite{glette} by 54.3\% in
simulation and 5.4\% in reality, and they outperformed gaits evolved
using HyperNEAT in hardware by 49.5\% (\tabref{results}).}
